---
title: CBB Best Ofs Episodes
date: "`r format(Sys.time(), '%d-%B-%Y')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "images/")

source("cbb-bestof-figure.R")
```

Comedy Bang Bang is an alt-comedy improv podcast published at least weekly since 2009. Each episode features one or more guests, who may be playing themselves or an improvised character. As of `r Sys.Date()`, there have been `r nrow(cbb)` mainline episodes with `r length(unique(all_guests))` unique guests.

At the end of the year, listeners vote on the best episodes of the year (Thanksgiving-to-Thanksgiving), which are compiled in year-end Best Of episodes that are published over the Christmas-New Year break. Paul F. Tompkins, the most frequent CBB guest, typically cohosts these shows with the show's host, Scott Aukerman.

I scraped the data directly from the Earwolf website using the `scrape-earwolf.R`, and then created the image via `cbb-bestof-figure.R`. The top 9 most frequently Best Of'd guests are highlighted by color, and the Best Of episodes are shaded grey.

```{r cbb-bestof-plot, fig.width = 12, fig.height = 6, warning = FALSE}
cbb_bestof_plot
```